{\LARGE \textbf{TÀI LIỆU THAM KHẢO}} \\[1cm] % Section 6

\begin{enumerate}[label={[{\arabic*}]}]
    \item Kusal, S., et al. (2022). A review on text-based emotion detection—Techniques, applications, datasets, and future directions. arXiv preprint arXiv:2205.03235. https://arxiv.org/abs/2205.03235

    \item Wu, W., Weng, J., Zhang, P., Wang, X., Yang, W., Jiang, J. (2022). URetinex-Net: Retinex-based deep unfolding network for low-light image enhancement. In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (pp. 5901–5910). https://byvn.net/rIFR

    \item Bie, M., et al. (2023). DA-FER: Domain adaptive facial expression recognition. Applied Sciences, 13(10), 6314. https://doi.org/10.3390/app13106314

    \item Al Hak, L. A., Ali, W. A., Saba, S. J. (2024). Facial expression recognition using data augmentation and transfer learning. Ingénierie des Systèmes d'Information, 29(3), 1219–1225. https://doi.org/10.18280/isi.290338

    \item Howard, A. G., et al. (2019). Searching for MobileNetV3. In Proceedings of the IEEE/CVF International Conference on Computer Vision (pp. 1314–1324). https://doi.org/10.1109/ICCV.2019.00140

    \item Liang, X., Liang, J., Yin, T., Tang, X. (2023). A lightweight method for face expression recognition based on improved MobileNetV3. IET Image Processing, 17(8), 2375–2384. https://byvn.net/wUkP

    \item Prasad, S. B. R., Chandana, B. S. (2023). MobileNetV3: A deep learning technique for human face expressions identification. International Journal of Information Technology. https://doi.org/10.1007/s41870-023-01380-x
    
    \item Ying, L., et al. (2017). A bio-inspired multi-exposure fusion framework for low-light image enhancement. IEEE Transactions on Image Processing, 26(12), 5932–5944. https://arxiv.org/abs/1711.00591
    
    \item Hu, J., Shen, L., Sun, G. (2018). Squeeze-and-excitation networks. In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (pp. 7132–7141). https://byvn.net/bnDA
    
\end{enumerate}